Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2018-05-09 WholePlotTrajectories.Rmd
Ref
Graphs, precise AGB loss

The functional redundancy was measured as the overlap among species in communities' functional space.
The samples of the trait database were first located with a PCA analysis in a two-dimensional functional space summarizing the 8 functional traits considered.
Then, multivariate kernel density estimator associated with individual trees were summed to give the distribution of traits probabilites of each species.
For each community the trait probability distributions of corresponding species were combined and weighted by species abundance. 
Eventually communities functional redundancy was measured as the sum of overlap between species weighted functional density.

@@

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Upper panels, Trajectories of the Simpson taxonomic diversity and Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. Lower panels, Relationship between the initial %AGB removed and the values of Simpson (c) and Rao (d) diversities at three times after disturbance. Solid lines colors represent the time, 10 years (yellow), 20 years (orange) and 30 years (brown) after disturbance.", fig.env="figure"}
load("DB/SimpsonDraw");load("DB/FunctionalTraj_ForGraphs")
load("DB/SimpsonIDH");load("DB/RaoIDH")

@@

plotIDH(Sim)
plotIDH(Rao)
mtext("initial %AGB lost",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.28,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

>>>>

The functional redundancy was measured as the overlap among species in communities' functional space [@Carmona2016].
The samples of the trait database were first located with a PCA analysis in a two-dimensional functional space summarizing the 8 functional traits considered.
Then, multivariate kernel density estimator associated with individual trees were summed to give the distribution of traits probabilites of each species.
For each community the trait probability distributions of corresponding species were combined and weighted by species abundance. 
Eventually communities functional redundancy was measured as the sum of overlap between species weighted functional density.

@@

```{r DivFun, out.width = '100%', echo=FALSE, fig.cap="Upper panels, Trajectories of the Simpson taxonomic diversity and Rao functional diversity over 30 years after disturbance. Trajectories correspond to the median (solid line) and 0.025 and 0.975 percentile (gray envelope) observed after 50 iteration of the taxonomic uncertainty propagation and the missing trait value filling processes. Initial treatments are represented by solid lines colors with green for control, blue for T1,orange for T2 and red for T3. Lower panels, Relationship between the initial %AGB removed and the values of Simpson (c) and Rao (d) diversities at three times after disturbance. Solid lines colors represent the time, 10 years (yellow), 20 years (orange) and 30 years (brown) after disturbance.", fig.env="figure"}
load("DB/SimpsonDraw");load("DB/FunctionalTraj_ForGraphs")
load("DB/SimpsonIDH");load("DB/RaoIDH");load("DB/LostAGB")

@@

plotIDH(Data=Sim,AgbLoss=AGBloss)
plotIDH(Data=Rao,AgbLoss=AGBloss)
mtext("initial %AGB lost",side=1,line=2.2,adj=1)
legend("right",inset=c(-0.28,0),xpd=NA,legend=c("10","20","30"),col=colyear,lwd=2.5,bty="n",title="Years")

### 2018-05-09 WholePlotTrajectories.tex
Graphs, precise AGB loss

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}.

These three indices belong to the set of HCDT or generalized entropy,
respectively corresponding to the 0, 1 and 2 order of diversity (q),
which proved well suited for diversity studies
\citep{Patil1982, Tothmeresz1995}. The functional diversity was reported
using the Rao index of quadratic entropy which combines species
abundance distribution and average pairwise dissimilarity based on all
functional and life traits.

>>>>

The taxonomic diversity was assessed through Richness and the Hill
number translation of Shannon and Simpson indices \citep{Hill1973}.
These three indices belong to the set of HCDT or generalized entropy,
respectively corresponding to the 0, 1 and 2 order of diversity (q),
which proved well suited for diversity studies
\citep{Patil1982, Tothmeresz1995}. The functional diversity was reported
using the Rao index of quadratic entropy which combines species
abundance distribution and average pairwise dissimilarity based on all
functional and life traits.

The functional redundancy was measured as the overlap among species in
communities' functional space \citep{Carmona2016}. The samples of the
trait database were first located with a PCA analysis in a
two-dimensional functional space summarizing the 8 functional traits
considered. Then, multivariate kernel density estimator associated with
individual trees were summed to give the distribution of traits
probabilites of each species. For each community the trait probability
distributions of corresponding species were combined and weighted by
species abundance. Eventually communities functional redundancy was
measured as the sum of overlap between species weighted functional
density.
